Object-oriented implementations of the MPDATA advection equation solver in~C++,~Python~and~Fortran

### 2013-01-16 paper/doc/paper.tex

  All codes are strucutred in a way allowing compilation of the code 
    in exactly the same order as presented in the text within one source file,
    hence every Fortran listing contains definition of a separate module.

>>>>

  All codes are structured in a way allowing compilation of the code 
    in exactly the same order as presented in the text within one source file,
    hence every Fortran listing contains definition of a separate module.
